Software architectures to integrate workflow engines in science gateways

### 2016-10-12 paper.tex
Finished new section 6

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Task encapsulation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow conversion. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{ardizzone2012decide},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, Neuroscience Gateway~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{kruger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in~\cite{kacsuk2014science}$^w$, GridSFEA~\cite{Elts2010}
            } \\
  Task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517}, Tavaxy~\cite{Abouelhoda2012}.
           }\\
  Conversion & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$, Tavaxy~\cite{Abouelhoda2012}, system in~\cite{delaGarza2016}.
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

Nested workflows are abstract architectural patterns that can be
instantiated in the various architectures described previously. We
focus on instantiation with the service invocation model
(Figure~\subref*{archi:nested}-Right) as this is the most used
architecture. In the instantiation, we assume that the parent and
child workflow engines are distinct pieces of software that require
different workflow services invoked by distinct \texttt{d}
interactions. If this is not the case, then workflow services can be
collapsed into a single one with a \texttt{d} interaction with
itself. An example of such interaction is the use of hierarchical
workflows in Pegasus~\cite{Deelman201517}.
Workflow engines communicate with infrastructures using
\texttt{b} and \texttt{c$_2$}. Science gateway transfers user data to
infrastructures using \texttt{c$_1$} interactions.

@@

@@

@@

\item Fine-grained debugging (\texttt{O$_2$}): availability of
  fine-grained debugging information about workflow tasks (white-box
  workflow).  Fine-grained information about workflow tasks is
  required to properly troubleshoot workflow executions. Its
  availability and accuracy usually depends on the number of software
  layers between the science gateway and the workflow
  engine~\cite{olabarriaga2014}. \texttt{O$_2$}=0 means that
  the information is directly accessible in the science gateway,
  \texttt{O$_2$}=1 means that it is obtained through one or more software
  interactions. 
\end{itemize}
\texttt{O$_1$} and \texttt{O$_2$} are summed to obtain a total number of missing specific
features in the architecture.

@@

\paragraph{Specific features} Task encapsulation explicitly enables
meta-workflows (\texttt{O$_1$}=0). Indeed, workflow engines may invoke
other engines using the exact same interaction used to submit regular
sub-tasks (interaction \texttt{e}), without any additional
development. Fine-grained debugging
information is obtained through interaction \texttt{b}
(\texttt{O$_2$}=1).

@@

\correction{To illustrate how our evaluation framework can be applied to the
design of new systems, let's consider a hypothetical system where the
workflow engine is split in two parts: (1) a high-level part
integrated in the science gateway, which submits sub-workflows to the
infrastructure; (2) a lower-level part, executed on the
infrastructure, which executes the sub-workflows. This scenario was
suggested by Reviewer \#2 of the paper after the evaluation framework
had been designed.

We model such a system using a nested workflow architecture where the
parent engine is tightly integrated in the science gateway, and the
child engine is integrated through task encapsulation.
Figure~\ref{fig:nested-3} shows the graphical representation of the
system. From this representation we find that the sub-tasks submitted
by the child engine through interaction \texttt{e} should be handled
by the parent engine rather than by the science gateway. Indeed,
handling the tasks directly in the science gateway would lead to
create a new specific interaction, named, e.g., \texttt{b$_1$}, while
\texttt{b} could be reused. We also find that interaction \texttt{e}
allows running the sub-tasks on the infrastructure supported by the
parent engine with no further development effort required in the child
engine.

The system evaluation is presented on
Table~\ref{table:evaluation-2}. The detailed calculations are
available in sheet ``Metrics with reviewer 2's architecture'' of the public spreadsheet.

We find that the studied system supports nested workflows with a much
better performance than the nested workflow model instantiated with
service invocation: the integration score is improved by a factor of
2, the robustness is improved by a factor of 2.6, the extensibility is
substantially improved, the scalability is not penalized, and the
specific features are slightly improved.}

\begin{figure}
  \centering
  \def\svgwidth{0.5\columnwidth}
  \input{figures/nested-3.pdf_tex}
  \caption{\correction{Nested workflow architecture instantiated with tight integration (parent engine) and task encapsulation (child engine).}}
  \label{fig:nested-3}
\end{figure}

\begin{table}
\footnotesize
\centering
\begin{tabular}{rc}
                                     & \textbf{Nested 1}\\
\cellcolor[HTML]{EEEEEE}\textbf{Integration complexity}&\cellcolor[HTML]{EEEEEE}\\
  Total components -- \texttt{I$_1$} & 2\\
Total interactions -- \texttt{I$_2$} & 6\\
\textbf{Total} (total software pieces) & \textbf{8}\\
\cellcolor[HTML]{EEEEEE}\textbf{Robustness}&\cellcolor[HTML]{EEEEEE}\\
Specific components -- \texttt{R$_1$} & 0\\
  Specific interactions -- \texttt{R$_2$} & 3\\
  \textbf{Total} (execution software pieces)& \textbf{3}\\
\cellcolor[HTML]{EEEEEE}\textbf{Extensibility}&\cellcolor[HTML]{EEEEEE}\\
  New engine type -- \texttt{E$_1$}  & 3\\
New engine version -- \texttt{E$_2$} & 1\\
  New workflow -- \texttt{E$_3$}     & 2\\
New infrastructure -- \texttt{E$_4$} & 4\\
  \textbf{Total} (difficulty to extend) & \textbf{10}\\
\cellcolor[HTML]{EEEEEE}\textbf{Scalability}& \cellcolor[HTML]{EEEEEE}\\
Multiple engine instances -- \texttt{S$_1$}& 1\\
Distributed engines -- \texttt{S$_2$}& 0\\
Task scheduling -- \texttt{S$_3$}    & 1\\
\textbf{Total} (scalability issues)  & \textbf{2}\\
\cellcolor[HTML]{EEEEEE}\textbf{Specific features}&\cellcolor[HTML]{EEEEEE}\\
  Meta-workflow  -- \texttt{O$_1$}    & 0\\
  Fine-grained debugging -- \texttt{O$_2$}  & 0.5\\
  \textbf{Total} (missing features) & \textbf{0.5}\\
\end{tabular}
\caption{\correction{Evaluation of the nested workflow architecture instantiated with tight integration (parent engine) and task encapsulation (child engine).}}
\label{table:evaluation-2}
\end{table}

@@

 Overall, task encapsulation performs a bit
better than the other architectures and nested workflows stand a bit
behind for the reasons mentioned previously.
\begin{table*}
\footnotesize
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Conversion} \\
  Integration (global score)    &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E899}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99D299}{0.44}
                                    & \cellcolor[HTML]{999999}{1.00}
                                      & \cellcolor[HTML]{99DD99}{0.33}\\
Robustness (global score) &
                                \cellcolor[HTML]{99F099}{0.14}
                                    & \cellcolor[HTML]{99D399}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99B699}{0.71}
                                    & \cellcolor[HTML]{999999}{1.00}
                                    & \cellcolor[HTML]{99D399}{0.43}\\
  Extensibility (global score)  & \cellcolor[HTML]{99D299}{0.44}
                                     & \cellcolor[HTML]{99D299}{\correction{0.22}}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99E899}{0.22}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99E899}{0.22}\\
Scalability (global score)  & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}\\
Specific features (global score) & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99DA99}\textbf{1.6}
                                    & \cellcolor[HTML]{99B899}\textbf{\correction{2.4}}
                                    & \cellcolor[HTML]{99FF99}\textbf{0.5}
                                    & \cellcolor[HTML]{99BF99}\textbf{2.4}
                                    & \cellcolor[HTML]{999999}\textbf{3.5}
                                    & \cellcolor[HTML]{99DE99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized global scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained as in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}

>>>>

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Task encapsulation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation (``Service+Service'').]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow conversion. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{ardizzone2012decide},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, Neuroscience Gateway~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{kruger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in~\cite{kacsuk2014science}$^w$, GridSFEA~\cite{Elts2010}
            } \\
  Task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517}, Tavaxy~\cite{Abouelhoda2012}.
           }\\
  Conversion & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$, Tavaxy~\cite{Abouelhoda2012}, system in~\cite{delaGarza2016}.
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

Nested workflows are abstract architectural patterns that can be
instantiated in the various architectures described previously. We
focus on instantiation with the service invocation model
(Figure~\subref*{archi:nested}-Right) as this is the most used
architecture. \correction{We call this instantiation
  ``Service+Service'' since both engines are integrated through
  service invocation.} We assume that the parent
and child workflow engines are distinct pieces of software that
require different workflow services invoked by distinct \texttt{d}
interactions. If this is not the case, then workflow services can be
collapsed into a single one with a \texttt{d} interaction with
itself. An example of such interaction is the use of hierarchical
workflows in Pegasus~\cite{Deelman201517}.  Workflow engines
communicate with infrastructures using \texttt{b} and
\texttt{c$_2$}. Science gateway transfers user data to infrastructures
using \texttt{c$_1$} interactions.

@@

&&&&& \textbf{\correction{Service+Service}}&\\

@@

                                     & \cellcolor[HTML]{99FF99}\correction{1}

@@

\item Fine-grained debugging (\texttt{O$_2$}): availability of
  fine-grained debugging information about workflow tasks (white-box
  workflow). \correction{We call ``white-box'' workflow a workflow
    where detailed information about individual tasks is available,
    for instance task statuses, execution logs and resource
    consumption. On the contrary, a ``black-box'' workflow only
    displays global information such as the workflow status and the
    logs of the workflow engine.} Fine-grained information about
  workflow tasks is required to properly troubleshoot workflow
  executions. \correction{It helps workflow users (scientists)
    identify errors, it allows gateway administrators to troubleshoot
    executions, and it facilitates debugging by workflow
    developers}. \correction{The availability and accuracy of
    fine-grained debugging information} usually depends on the number
  of software layers between the science gateway and the workflow
  engine~\cite{olabarriaga2014}. \texttt{O$_2$}=0 means that the
  information is directly accessible in the science gateway,
  \texttt{O$_2$}=1 means that it is obtained through one or more
  software interactions.
\end{itemize}
\texttt{O$_1$} and \texttt{O$_2$} are summed to obtain a total number of missing specific
features in the architecture.

@@

\paragraph{Specific features} Task encapsulation \correction{does not enable meta-workflows by default (\texttt{O$_1$=1})}. Fine-grained debugging
information is obtained through interaction \texttt{b}
(\texttt{O$_2$}=1).

@@

\correction{To illustrate how our evaluation framework can be applied
  to the design of new systems, let's consider a hypothetical system
  where the workflow engine is split in two parts: (1) a high-level
  part integrated in the science gateway, which submits sub-workflows
  to the infrastructure; (2) a lower-level part, executed on the
  infrastructure, which executes the sub-workflows. This scenario came
  up in the discussion with Reviewer \#2 of this paper, after the
  evaluation framework had already been designed.

  We model such a system using a nested workflow architecture with a
  ``Tight+Task'' instantiation, i.e., the parent engine is tightly
  integrated in the science gateway and the child engine is
  integrated through task encapsulation.  Figure~\ref{fig:nested-3}
  shows the graphical representation of the system. From this
  representation we find that the sub-tasks submitted by the child
  engine through interaction \texttt{e} should be handled by the
  parent engine rather than by the science gateway. Indeed, handling
  the tasks directly in the science gateway would lead to create a new
  specific interaction, named, e.g., \texttt{b$_1$}, while \texttt{b}
  could be reused. We also find that interaction \texttt{e} allows
  running the sub-tasks on the infrastructure supported by the parent
  engine with no further development effort required in the child
  engine.

The system evaluation is presented on
Table~\ref{table:evaluation-2}. The detailed calculations are
available in sheet ``Metrics with reviewer 2's architecture'' of the public spreadsheet at \url{https://frama.link/LrPRsCQp} \todo{revise that sheet to merge it with the main one}.

We find that the studied system supports nested workflows with a much
better performance than the nested workflow model instantiated with
service invocation (evaluated on Table~\ref{table:evaluation}): the
integration score is improved by a factor of 2, the robustness is
improved by a factor of 2.6, the extensibility is substantially
improved, the scalability and specific features are not penalized.

Based on this system, we propose a new system design that instantiates
the nested workflow model in a ``Task+Task'' way, i.e., with task
encapsulation for both the parent and the child engine. The
architecture of this system is represented in
Figure~\ref{fig:nested-4}. The diagram is identical to the one in
Figure~\ref{archi:sub-task}, except that interaction \texttt{e} is now
used to submit sub-workflows instead of just sub-tasks. This is
possible since, in the task encapsulation architecture, workflows are
executed as tasks.

The new architecture performs better similarly to task encapsulation,
except that it now enables meta-workflows and distributed engines
which were not available previously. It clearly outperforms the nested
``Service+Service'' architecture.

Based on this analysis, we plan to extend the PSOM-CBRAIN integration
to support this architecture. Conceptually, the implementation is
simple, as it only requires existing workflows to be declarable as
tasks in the workflow engine. In practice, technical issues may delay
the process. We also remain well aware of the scheduling issues raised
by the task encapsulation architecture (S$_3$=1), which will be
amplified in the ``Task+Task'' instantiation of nested workflows: for
instance, properly setting resource requirements (e.g. walltime) is
increasingly difficult when nested workflow engines are deployed on
the infrastructure.  }

\begin{figure}
  \centering
\subfloat[Nested, Tight+Task]{
  \def\svgwidth{0.5\columnwidth}
  \input{figures/nested-3.pdf_tex}
  \label{fig:nested-3}
}
\subfloat[Nested, Task+Task]{ 
  \def\svgwidth{0.5\columnwidth}
  \input{figures/sub-task.pdf_tex}
  \label{fig:nested-4}
}
\caption{\correction{Nested workflow architecture instantiated with tight integration and task encapsulation (top) and task encapsulation only (bottom).}}
\label{fig:new-systems}
\end{figure}

\begin{table}
\footnotesize
\centering
\begin{tabular}{rcc}
                                     & \textbf{Nested} & \textbf{Nested}\\
                                     & \textbf{Tight+Task} & \textbf{Task+Task}\\
\cellcolor[HTML]{EEEEEE}\textbf{Integration complexity}&\cellcolor[HTML]{EEEEEE}&\cellcolor[HTML]{EEEEEE}\\
  Total components -- \texttt{I$_1$} & 2 & 2 \\
Total interactions -- \texttt{I$_2$} & 6 & 5 \\
\textbf{Total}& \textbf{8} & \textbf{7}\\
\cellcolor[HTML]{EEEEEE}\textbf{Robustness}&\cellcolor[HTML]{EEEEEE}&\cellcolor[HTML]{EEEEEE}\\
Specific components -- \texttt{R$_1$} & 0 & 0\\
  Specific interactions -- \texttt{R$_2$} & 3 & 1\\
  \textbf{Total}& \textbf{3} & \textbf{1}\\
\cellcolor[HTML]{EEEEEE}\textbf{Extensibility}&\cellcolor[HTML]{EEEEEE}&\cellcolor[HTML]{EEEEEE}\\
  New engine type -- \texttt{E$_1$}  & 3 & 2\\
New engine version -- \texttt{E$_2$} & 1 & 1\\
  New workflow -- \texttt{E$_3$}     & 2 & 2\\
New infrastructure -- \texttt{E$_4$} & 4 & 3\\
  \textbf{Total}& \textbf{10} & \textbf{8}\\
\cellcolor[HTML]{EEEEEE}\textbf{Scalability}& \cellcolor[HTML]{EEEEEE}&\cellcolor[HTML]{EEEEEE}\\
Multiple engine instances -- \texttt{S$_1$}& 1 & 0\\
Distributed engines -- \texttt{S$_2$}& 0 & 0\\
Task scheduling -- \texttt{S$_3$}    & 1 & 1\\
\textbf{Total}& \textbf{2} & \textbf{1}\\
\cellcolor[HTML]{EEEEEE}\textbf{Specific features}&\cellcolor[HTML]{EEEEEE}&\cellcolor[HTML]{EEEEEE}\\
  Meta-workflow  -- \texttt{O$_1$}    & 0 & 0\\
  Fine-grained debugging -- \texttt{O$_2$}  & 1 & 1\\
  \textbf{Total}& \textbf{1} & \textbf{1}\\
\end{tabular}
\caption{\correction{Evaluation of the nested workflow architecture instantiated with tight integration (parent engine) and task encapsulation (child engine).}}
\label{table:evaluation-2}
\end{table}

@@

 Overall, task encapsulation performs a bit
better than the other architectures and nested workflows stand a bit
behind for the reasons mentioned previously.
\begin{table*}
\footnotesize
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Conversion} \\
                                    &&&&& \textbf{\correction{Service+Service}}&\\
  Integration (global score)    &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E899}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99D299}{0.44}
                                    & \cellcolor[HTML]{999999}{1.00}
                                      & \cellcolor[HTML]{99DD99}{0.33}\\
Robustness (global score) &
                                \cellcolor[HTML]{99F099}{0.14}
                                    & \cellcolor[HTML]{99D399}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99B699}{0.71}
                                    & \cellcolor[HTML]{999999}{1.00}
                                    & \cellcolor[HTML]{99D399}{0.43}\\
  Extensibility (global score)  & \cellcolor[HTML]{99D299}{0.44}
                                     & \cellcolor[HTML]{99D299}{\correction{0.22}}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99E899}{0.22}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99E899}{0.22}\\
Scalability (global score)  & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}\\
Specific features (global score) & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99DA99}\textbf{1.6}
                                    & \cellcolor[HTML]{99B899}\textbf{\correction{2.4}}
                                    & \cellcolor[HTML]{99FF99}\textbf{0.5}
                                    & \cellcolor[HTML]{99BF99}\textbf{2.4}
                                    & \cellcolor[HTML]{999999}\textbf{3.5}
                                    & \cellcolor[HTML]{99DE99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized global scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained as in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}
